On the error performance of the $A_n$ lattices

### 2011-12-04 paper.tex
removed unnesecary stuff.  Added some instructions to README.

We now plot the probability of coding error versus signal to noise ratio (SNR) for the lattices $A_1, A_2, A_3, A_4$ and $A_5$.  For these plots the SNR is related to noise variance according to~\cite{Viterbo_diamond_cutting_1996}
\[
\text{SNR} = \frac{V^{2/n}}{4\sigma^2},
\]
where $V$ is the volume of the Voronoi cell and $n$ is the dimension of the lattice.  Figure~\ref{fig:peplots} shows the `exact' probability of error (correct to 16 decimal places) computed using the moments $\calM_n(m)$ and~\eqref{eq:summomentproberror} (solid line).  The number of moments needed to ensure a certain number of decimal places accuracy depends on $n$ and also on the noise variance $\sigma^2$.  At most 252 moments where needed for Figure~\ref{fig:peplots}.  We also display the probability of error computed approximately by Monte-Carlo simulation (dots).  %We have used the fast nearest point algorithm for $A_n$ described in~\cite{McKilliam2009CoxeterLattices} and~\cite[p. 448]{SPLAG}.
The simulations are iterated until 500 error events occur.

@@

\begin{figure*}[tp]
	\centering
		\includegraphics{plots/peplots-1.mps}
		\caption{The probability of error versus SNR for $A_1 \simeq \ints$, $A_2$, $A_3\simeq D_3, A_4, A_5$ and $E_8$.}
		\label{fig:peplots}
\end{figure*}

>>>>

We now plot the probability of coding error versus signal to noise ratio (SNR) for the lattices $A_1, A_2, A_3, A_4, A_5$ and $A_8$.  For these plots the SNR is related to noise variance according to~\cite{Viterbo_diamond_cutting_1996}
\[
\text{SNR} = \frac{V^{2/n}}{4\sigma^2},
\]
where $V$ is the volume of the Voronoi cell and $n$ is the dimension of the lattice.  Figure~\ref{fig:peplots} shows the `exact' probability of error (correct to 16 decimal places) computed using the moments $\calM_n(m)$ and~\eqref{eq:summomentproberror} (solid line).  The number of moments needed to ensure a certain number of decimal places accuracy depends on $n$ and also on the noise variance $\sigma^2$.  At most 321 moments where needed for Figure~\ref{fig:peplots}.  We also display the probability of error computed approximately by Monte-Carlo simulation (dots).  %We have used the fast nearest point algorithm for $A_n$ described in~\cite{McKilliam2009CoxeterLattices} and~\cite[p. 448]{SPLAG}.
The simulations are iterated until 500 error events occur.

@@

\begin{figure*}[tp]
	\centering
		\includegraphics{plots/peplots-1.mps}
		\caption{The probability of error versus SNR for $A_1 \simeq \ints$, $A_2$, $A_3\simeq D_3, A_4, A_5, A_8$ and $E_8$.}
		\label{fig:peplots}
\end{figure*}
